%-------------------------
% Resume in Latex
% Author : Dakota McDanils
% License : MIT
%------------------------

\documentclass[a4paper]{article}

\usepackage{latexsym}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage[
  margin=2.2cm,
  includefoot,
  footskip=30pt,
]{geometry}
\usepackage{layout}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.4in}
\addtolength{\evensidemargin}{-0.4in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.4in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://dakot.ai/}{\Large Dakota McDaniels}} & Email : \href{mailto:dakotajmcd@gmail.com}{dakotajmcd@gmail.com}\\
  \href{http://dakot.ai/}{dakot.ai} & Mobile : +1-803-422-5536 \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart
  
	\resumeSubheading
 	{Pluto}{San Francisco, CA}
 	{Co-Founder and Co-CTO}{May 2021 - August 2023}
		\resumeItemListStart
			\resumeItem{Fundraising and Leadership}{}
				\begin{itemize}
					\item Secured \$5M in funding to accelerate the growth and development of the AI financial advisory platform.
					\item Grew the user base to over 30,000 while scaling the platform to manage over \$40M in user-linked assets.
					\item Led a hiring initiative, conducting 100+ interviews and building a team of 10 key employees.
				\end{itemize}
			\resumeItem{Infrastructure and Cloud Computing}{}
				\begin{itemize}
					\item Architected and deployed 50+ microservices and cron jobs in Python, utilizing CircleCI for automated deployments.
					\item Managed a robust Kubernetes environment on Digital Ocean, sustaining over 1,000 auto-scaling pods.
					\item Developed a Kafka-based order management system, processing over 100,000 transactions daily, equating to more than \$100M in daily trading volume.
					\item Sustained 99.99\% system uptime through comprehensive monitoring protocols, ensuring high availability and reliability.
				\end{itemize}
			\resumeItem{Product Development and AI Innovation}{}
				\begin{itemize}
					\item Launched a cutting-edge platform for practical and live trading of US equities and cryptocurrencies, leveraging advanced AI to drive user engagement and investment efficiency.
					\item Introduced the first AI financial assistant, reducing data "hallucinations" by 90\% and increasing response quality by 80\%, using CoT, RAG, and ReAct techniques.
					\item Created a proprietary Domain-Specific Language (DSL) for LLMs, enabling command generation for stock prices, news updates, and portfolio management.
				\end{itemize}
		\resumeItemListEnd

	\resumeSubheading
    {Lowe's}{Mooresville, NC}
	{Information Security Analyst}{May 2020 - May 2021}
		\resumeItemListStart
			\item Published minimum security baselines for 180,000+ instances including operating systems, applications, and PCI-DSS compliant devices. 
			\item Designed security baselines for multiple Linux distros, NoSQL databases, NGINX, and PostgREST.
			\item Led security compliance monitoring across a 70-team organization through routine reporting and notifications.
		\resumeItemListEnd

	\resumeSubheading
	{University of South Carolina}{Columbia, SC}
	{Internship – Networking Technician and Networking Engineer}{October 2018 - December 2020}
		\resumeItemListStart
			\item Supervised and mentored nine Computer Science interns, directing project workflows over six months.
			\item Resolved 445 network and security incidents, accounting for 42.5\% of the internship program’s total output.
			\item Managed network infrastructure with over 850 switches and 4,100 access points across the campus using industry-standard tools like SolarWinds, Cisco, and Aruba ClearPass.
		\resumeItemListEnd
		
	\resumeSubheading
	{Office of Naval Research}{Columbia, SC}
	{Undergraduate Research in Cyber Security}{August 2020 - October 2020}
		\resumeItemListStart
			\item Researched DDoS attack mitigation using Palo Alto’s next-generation firewalls.
			\item Developed training materials for CI engineers on high-throughput, low-latency network environments.
			\item Awarded part of the \$499,959.00 grant for "Cyberinfrastructure Expertise on High-throughput Networks for Big Science Data Transfers" (NSF 1829698).
		\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
    \resumeSubHeadingListStart
		\resumeSubItem{Quantitative Securities Trading System}
			\resumeItemListStart
				\item Built a performant, event-sourced data pipeline for backtesting and live-trading with Python and Jupyter Labs.
				\item Conducted extensive backtests with over 700,000 minutes of historical trading data to validate investment strategies.
				\item Deployed a secure AWS infrastructure using ECS and Docker to manage over \$50,000 of personal investment capital.
			\resumeItemListEnd
		\resumeSubItem{BetterReplies}{An iOS app featuring a fine-tuned AI assistant capable of generating personalized replies}
			\resumeItemListStart
				\item Developed with Python and SwiftUI, automatically deployed using GitHub Actions and Terraform.
				\item Integrated a robust, cloud-native backend architecture on AWS, including ECR, Lambda, S3, and API Gateway.
				\item Performed comparative analysis of LLM providers such as OpenAi, Anthropic, and LLaMa to optimize AI response quality.
			\resumeItemListEnd
    \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
 \section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}: Python, Swift, SQL, Terraform
      \hfill
      \textbf{Cloud Providers}: AWS, Digital Ocean, Heroku
    }
    \item \textbf{Databases}: MongoDB, Postgres, Supabase 
	\item \textbf{Technologies}: Redis, REST, Kafka, Kubernetes, Git, Flask, CircleCi, Github Actions
	\item \textbf{LLMs}: Prompt Engineering, Fine-tuning, Data Gathering, Retrieval-Augmented Generation, Chain-of-Thought 
	\item \textbf{Paradigms}: Functional Programming, OOP, Microservices, Infrastructure as Code, Cloud Native, CI/CD
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}