%-------------------------
% Resume in Latex
% Author : Dakota McDanils
% License : MIT
%------------------------

\documentclass[a4paper]{article}

\usepackage{latexsym}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage[
  margin=2.2cm,
  includefoot,
  footskip=30pt,
]{geometry}
\usepackage{layout}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.4in}
\addtolength{\evensidemargin}{-0.4in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.4in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.4cm]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://dakot.ai/}{\Large Dakota McDaniels}} & Email : \href{mailto:dakotajmcd@gmail.com}{dakotajmcd@gmail.com}\\
  \href{http://dakot.ai/}{dakot.ai} & Mobile : +1-803-422-5536 \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart
  
	\resumeSubheading
	{Pluto.fi}{San Francisco, CA}
 	{Co-Founder and Co-CTO}{May 2021 - August 2023}
		\resumeItemListStart
			\resumeItem{Fundraising and Leadership}{}
				\begin{itemize}[leftmargin=0.35cm]
					\item Raised \$5M in VC funding to build and scale Pluto's AI financial advisory product.
					\item Scaled the technology and team to support 25,000 users and over \$40M in tracked assets.
					\item Conducted 100+ interviews after sourcing candidates from AngelList, recruiters, and inbound applications.
					\item Hired a team of 3 engineers and product designers.
				\end{itemize}
			\resumeItem{Infrastructure and Cloud Computing}{}
				\begin{itemize}[leftmargin=0.35cm]
					\item Architected and deployed 50+ K8s microservices and cron jobs alongside CI/CD with CircleCI.
					\item Managed a 30 node Kubernetes cluster with over 1TB of RAM to support a 10,000 pod workload.
					\item Built an order management system to process 12.5M trading decisions every hour using Kafka.
					\item Achieved 99.99\% system uptime through comprehensive monitoring and observability.
					\item Engineered a high-performance database architecture using MongoDB and Redis, which supported ultra-high transaction volumes of 100+ million per month with average latency under 10ms.
				\end{itemize}
			\resumeItem{Product Management and AI Innovation}{}
				\begin{itemize}[leftmargin=0.35cm]
					\item Single-handedly streamlined the entire brokerage integration process to operational readiness in just 14 days – covering payment rails, KYC, order management, and compliance – shattering the typical 6-month timeline for a traditional team of 10.
					\item Overhauled the user onboarding experience, simplifying KYC and deposit/withdrawal processes, which increased user conversion rates by 30\%.
					\item Introduced the first AI financial assistant that uses advanced NLP techniques like CoT, RAG, and ReAct to provide accurate and contextually relevant responses to user queries.
					\item Implemented measures to reduce irrelevant or inconsistent responses by 90\%, significantly improving user experience and engagement.
					\item Pioneered an AI-powered UI that generates real-time charts and insights based on user prompts for a wide range of financial topics, from individual stock performance to market trends.
				\end{itemize}
		\resumeItemListEnd

	\resumeSubheading
    {Lowe's}{Mooresville, NC}
	{Cybersecurity Engineer}{May 2020 - May 2021}

	\resumeSubheading
	{University of South Carolina}{Columbia, SC}
	{Internship – Network Security Engineer}{October 2018 - December 2020}

	\resumeSubheading
	{Office of Naval Research}{Columbia, SC}
	{Undergraduate Research in Cybersecurity}{August 2020 - October 2020}

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
    \resumeSubHeadingListStart
		\resumeSubItem{Quantitative Securities Trading System}
			\resumeItemListStart
				\item Built a performant, event-sourced data pipeline for backtesting with over 700M minutes of historical tick data in Python.
				\item Deployed a secure AWS infrastructure on ECS and Docker to manage over \$50,000 of personal investment capital.
			\resumeItemListEnd
		\resumeSubItem{BetterReplies}{An iOS app featuring a fine-tuned AI assistant capable of generating personalized replies}
			\resumeItemListStart
				\item Developed with Python and SwiftUI, automatically deployed using GitHub Actions and Terraform.
				\item Integrated a robust, cloud-native backend architecture on AWS, including ECR, Lambda, S3, and API Gateway.
				\item Performed comparative analysis of LLM providers such as OpenAi, Anthropic, and LLaMa to optimize AI response quality.
			\resumeItemListEnd
    \resumeSubHeadingListEnd


%--------EDUCATION------------
 \section{Education}
  \resumeSubHeadingListStart
	\resumeSubheading
	{University of South Carolina}{Columbia, SC}
	{Bachelor of Science}{August 2018 - December 2020}
		\resumeItemListStart
			\item Degree in Integrated Information Technology (Hybrid degree for Computer Science and Cybersecurity)
			\item Major GPA of 4.0, Overall GPA of 3.986
		\resumeItemListEnd
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
 \section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}: Python, Swift, SQL, Terraform
      \hfill
      \textbf{Cloud Providers}: AWS, Digital Ocean, Heroku
    }
    \item \textbf{Databases}: MongoDB, Postgres, Redis, Pinecone, Supabase
	\item \textbf{Technologies}: REST, Kafka, Kubernetes, Git, Flask, CircleCi, Github Actions
	\item \textbf{LLMs}: Prompt Engineering, Fine-tuning, Data Gathering, Retrieval-Augmented Generation, Chain-of-Thought 
	\item \textbf{Paradigms}: Functional Programming, OOP, Microservices, Infrastructure as Code, Cloud Native
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}